\section{Docker and Git}
At the beginning of the project, it was chosen to use docker to develop the system, this meant that the program would be identical on each computer, a bit like a virtual machine.
Docker thus helped by having identical runs of the program, which resulted in easier isolation of problems and thus propelled the project forward at a faster pace.
However, this also created problems because "docker" was implemented with mediocre knowledge of the technology, causing minor problems all around.
In addition, the startup for docker was also slow, making the time from writing code to seeing the result stretched.
It can be said that Docker was smart in the intention of a more stable development, but better knowledge of the technology should be gathered beforehand.
% Rasmus: Hvilken viden manglede der i implementeringen af docker? Tror ikke der var en meget bedre måde for alle at lære det på end at bruge dem.

It can also be said that the version control system git, helps in similar ways.
So it would not be necessary to use both systems as it leads to bloated complexity in development.
% Rasmus: What? Skulle vi ikke have brugt versionsstyring?
In the project github page, pull requests were also used.
Pull requests work by notifying their team members of the changes they have made, which these group members can then assess and allow to move into the program.
Looking back, you can say that there was probably enough security in the project via git.
% Rasmus: Jeg ved ikke helt hvad det her afsnit betyder