%BACKGROUND INFO OR DOCUMENT MANAGEMENT IS NEEDED BECAUSE????
In most industries there are set of standards for how things are done.
These standards range from  entirely voluntary to required by law, depending on the legislation in the specific area.
Each standard has a set of requirements that a company has to adhere to in order to get a ceritificate stating so.
Whether this is done correctly is checked during an audit where a professional auditor examines the company.

This project is based upon a case presented by Pia Ipsen, a quality management consultant.
Quality management is a challenge across multiple industries: For instance Ipsen works with both a cheese slicing and a shipping company.
Generally speaking, quality management will involve document management.
% Anja: Maaske skriv noget om, at dette document management halløj raader over haandbøger? Jeg tænker, at der skal noget mere tekst om, at det handler om haandbøger
%Astrid: Tanken var at kun det meget brede hvad er emnet overhovedet blev præsenteret heroppe og saa kommer den mere specifikke hvad er haandbogen under key terms 

%IDENTIFY NEED FOR MORE
Multiple document management systems already exist, but as none of them fit the needs of the companies she works with she does not use any of them.
Her priorities are:

\begin{itemize}
\item Simplicity. The learning curve should be fast and the system should support the file formats and work flow presently in use.
%Anna: Det med file formats er ikke et strengt krav (det blev bekræftet på sidste møde)
\item Cost. A reason to not use an existing system is that they are too expensive when compared to the expected output.
\end{itemize}

%INTRODUCE KEY TERMS / STATE AIM
The documents in question being managed are those in the company handbook; a collection of instructions on how things are supposed to be done specific to the company.
Before a document is added to the handbook it has to go through an approval system.
To ensure that everyone has read the required document, a monitoring system is needed.
%Anna: Er det virkeligt korrekt at sige det ligefrm er nedded (da det var noget som Rasmus snakkede om og hun kom til at se værdi i)?
Additionally document management entails version and access control as well as the ability to provide access to earlier versions of the documents.

%SCOPE THIS SHIT/LIMITATIONS
Multiple related problems exist: Marking the exact differences between versions and maintaining control of documents related to the approval of suppliers among those.
However these things are outside the scope of the project.
%Anna: synes den sidste sætning skal slettes da det er noget vi afgrænser os væk fra i løbet af rapporten og derfor ikke ngoet som ikke har været en del af projektet

%INDICATE PLANS (HOW THE F IS IT POSSIBLE TO MAKE SOMETHING THIS BRILLIANT)
%The problem is examined through interviews and tests

%Anna: Evt ikke lave det til en del afsnit men inkluder initial problemstatement direkte i teksten som safsluttende i stedet for (Virker tyndt med kun ot linjer i en section)