\subsection{Dropbox}
\todo[inline]{Der mangler kilder :-)}
Dropbox is a file hosting service that allows the user to place files on remote servers using the client or using the web interface through a browser.
Installing the Dropbox client software creates a folder on your computer, that keeps the files inside synchronized with the Dropbox servers.
Although the focus of the technology is on synchronization and information exchange, Dropbox also keeps a download history so that after deleting files from the server it is possible to recover data.
A file change history is also kept, which is available for the period of the last 30 days.
The history of file changes is based on the principle of diff-coding, in order to save the space occupied by the files.
In the change history, only the difference of one version of the file from another is recorded.
There is also the ability to upload files for sharing through the “Public” folder, which allows you to use the service as a file sharing service.
For collaboration on projects, the service can create “Shared” folders for public access for persons with different accounts on the service.
Available automatic synchronization of files and folders and version storage with the ability to roll back.
For users of Dropbox Professional and Dropbox Business, Smart Sync functionality is available, which saves hard disk space by displaying only the names and information about files without downloading their contents.
Unlike several analogues, Dropbox does not use data encryption on the client side, which made possible the incident of June 19, 2011, when due to an error in the updated server software, it was possible to log into any account using the account for four hours using any password. (https://techcrunch.com/2011/06/20/dropbox-security-bug-made-passwords-optional-for-four-hours/)
The service offers 2 GB free for data storage, which can be increased free up to 16 GB, inviting new users or getting a few gigabytes after completing tasks (installing the Dropbox application on a mobile phone, etc.). And you can also buy 1 TB.
