When developing a new system it is important to explore existing systems.
This is to ensure that the designers and developers know which solutions already exist and thereby how the future solution is going to fit into the technological landscape.
It is also beneficial to explore exisiting solutions as these can give the designers knowledge about the design convention within the area and perhaps new ideas to explore.
%bør der evt. være en kilde her?
%astrid: evt undgå med omformulering? "To get inspiration for the new system some existing solutions were examined"?
For this case the report asks the following questions when exploring an existing system \citep[p.~33]{Rod-Aalborg}:

\begin{itemize}
  \item Which ideas lay the groundwork for the system?
  \item Do the ideas seem useful? Why?
  \item Will the ideas work in your context? Why?
  \item Can the ideas be adapted to your system? How?
\end{itemize}

The systems this report will look into in this section are a couple of existing systems that specialize in handbook management are; \textit{BlissBooks} and \textit{D4Handbooks}, as well as the more general document management systems; \textit{Google Drive} and \textit{Dropbox}. All the systems were tried, besides \textit{D4Handbooks}, which did not have a publicly available trial version. That chapter is largely based on sales material, which naturally causes a bias.

Many of the solutions introduced are Software as a Service (SaaS). This refers to software which is not downloaded and run on the users computer, as traditional software, but rather runs in the browser, with much of the backend work happpening on the owner of the softwares server.
\todo[inline]{Astrid: Lav en forward ref til hvad Pia vil have}
