\section{Problem Statement} \label{problemstatement}
Throughout this chapter the case and the consequent analysis has been explored.
%Anna: Vil rigtig gerne slette resten af det her afsnit og istedet sætte linjen ovenover sammen med afsnittet nedenfor
This has led to descriptions of the case, ISO-standards, exisiting solutions, and a rich picture and FACTOR-analysis, see \cref{sec:CaseDescription,sec:standards,chap:existing,sec:richpictures,sec:factorcriteria}.

The case presented by Ipsen is the main problem that the project works to solve through the design and development of a system that supports the management and versioning of handbook documents. 
The following exploration of existing solutions outlines the current technological landscape in relation to handbook management which could potentially give inspiration to design of the future system and help differentiate it.
%Anna: Burde man på det her tidspunkt ikke nævne nogen af de ting der var værd at bruge som inspiration
By the end of the chapter an in-depth analysis of Ipsen's first two interviews were made through rich pictures and the FACTOR criterion.

This problem analysis has lead to the following problem statement:

\begin{center}
\textit{How can a document version management software be designed and developed to support a firm's management of their handbook documents so it is easily manageable by the administrators, and also accessible for readers and writers?}
\end{center}
%Anna: Ved godt vi ikke skulle snakke formuleringer med synes den sætning bliver kringlet og ordet manage står mange gange i streg

The rest of the project as well as  the system developed as a part of it will seek to answer this statement.
There are several aspects of the statement to consider during the process.
These are:
\begin{itemize}
	\item 
		\textit{Document version management:} 
		The software must be able to manage documents and their versions.
	\item 
		\textit{Design and development:} 
		There are two main processes that the project group must undergo through the project which are the design processes and the development of the system based on the design.
	\item 
		\textit{Administrators, readers, and writers:} 
		There are different roles associated with the system that needs to be considered both during the design and development process.
\end{itemize}
%Anna skal Design og development ikke enten være den første eller den sidste?
%Anna: Den med rollerne starter med at skrive de tre roller og nedenunder står der noget med different roles (hvad er tanken bag det)
%anna: Bliver de her punkter diskuttert og ikke mindst konkluderet på?