\subsection{Entity Framework Core}
EF Core is used to communicate with the database, which on its own is not object-oriented.
For more information on EF Core see \cref{sec:efcore}.

Postgresql was chosen as the database for this development project.
The decision was purely based on prior experiences with setting up such a database.
Postgresql is often better suited for more advanced applications, {\color{red}[CITATION NEEDED]} but as this application mostly uses CRUD operations with few to no complicated queries, this was hardly relevant.

\subsubsection{HandbookContext}
The \texttt{HandbookContext} is the class that handled communication between the database and the application.
It subclasses IdentityDbContext, which in turn subclasses a normal DbContext.
\lstinputlisting[caption={HandbookContext}, language={[Sharp]C}]{OBHandbooks/OBHandbooks/Infrastructure/HandbookContext.cs}
%Anna: igen grundet listings længden kunne det give mening at ligge den i appendiks?
%Taniya: meget kort forklaring til en meg meg lang listing. Anyways, hvad er modelBuilder for noget?
It consists of a large amount of properties of the type \texttt{DbSet<MODEL>}, which each represents a collection of entities to be stored in the database. 
The overwritten \texttt{OnModelCreating} function also supplies extra information about the relationships in the database, such as unique properties, foreign keys, or delete behaviours. For example, on line 31, it can be seen that when a \texttt{HandbookApproval} is to be deleted it should also result in any associated \texttt{Version} objects being deleted.

\input{Chapters/Implementation/RepositoryPattern}
\subsubsection{Database Design}
\todo[inline]{Andreas: Gør den der ting jeg bad dig om}
The database design should hopefully look a lot like the class diagram.
