\section{Navigation Tree}
\todo[inline]{Taniya: Skriv "the" foran page navnene}
This section describes the navigation tree that visualizes how user move through the application, see \Cref{fig:Navigation}.
\input{Chapters/Design/navigation}

The user will first encounter the login page.
For the first-timer user they have to enter the Activate account page and insert the given username received from administrator to register email address (optional) and create a password.
Once activate account process is finished user will be redirected to handbook's main page.
If the account is already activated user will be redirected to the main page once logged in.

In the main page administrator and writer will be able to access the ``Add new document'' page.
Writer will be able to access awaiting approvals under the relevant document section in the main page.
Administrator will be able to enter Approvals page through a sidebar which is only accessible for administrator.
The sidebar consists of:

\begin{itemize}
	\item Handbook (return to the main page)
	\item Approvals
	\item Archive
	\item User administration
	\item Departments
	\item Settings
\end{itemize}

Preview document page can be access in three ways depends on access rights, see \Cref{tab:docPreviewEntries} below.

\begin{table}[H]
	\begin{center}
	\begin{tabular}{| m{20em} | c | c | c | c | c |}
		\hline
		Document preview entry & Administrator & Writer & Reader \\
		\hline
		 Directly through document in the valid handbook & x  & x & x\\
		\hline
		 Through archive document  & x &  & \\
		\hline
		 Via awaiting approval document & x & x &  \\
		\hline
	\end{tabular}
	\end{center}
	\caption{Document preview entries}\label{tab:docPreviewEntries}
\end{table}

Through User administration page which is accessible from the sidebar administrator will be able to access Create user page or User info page to enter Edit page and update user information.

Under Departments page entered through the sidebar.
Administrator will be able to click on existing department name to enter Detail page of an overview of associate users and documents.
In the overview page administrator would be able to enter Edit users page or Edit documents page.

Settings page is accessible from the sidebar where administrator can change the company name and enable or disabled changelog functionality to the application.

In the Navigation tree in \Cref{fig:Navigation} the read box indicate that every role can enter Edit profile page or Log out on the global, top-level navigation bar anywhere in the navigation flow within the red box.
