\section{ISO}
This section covers the most widely used standards worldwide [], which includes explanation of what ISO standards contain, their purposes and benefits, as well as why ISO standards are relevant to the handbook version control system. This section is based on [] unless otherwise stated.

International Organization for Standardization (ISO) is a non-governmental organization that develops and produces International Standards in various fields. The ISO standards are created by leading experts globally, so the knowledge is shared and negotiated. ISO seeks to meet the needs of the market; new standards will be developed if they are requested by an industry or consumer groups. An ISO standard is a document consisting of practical information, requirements, specifications, guidelines, and best practices. 

The general purpose of ISO standards is to create safe, reliable and good quality products and services including improving the efficiency of the business which results in minimizing waste, errors and reducing production costs. This way business could gain consumer confidence, promote best practices to fill knowledge gaps, and optimize resource utilization. The ISO standards also provide solutions to challenges such as environment issues and sustainability. 

There exist various types of ISO standards from Risk Management standards to Safety and Healthcare standards. The most well-known are listed below.

\begin{itemize}
	\item ISO 9000 Family - Quality Management
	\item ISO 22000 Food Safety Management
	\item ISO 14000 Family - Environmental Management

\end{itemize}

It is relevant to look further into the ISO 9001 which is a Quality Management System that is suitable to any business or organization regardless of size and industry. The ISO 9001 standard sets criteria for a quality management system that contributes to the improvement of efficiency and customer satisfaction. The Quality Management System is based on Quality Management Principles that contain customer focus, leadership and employee engagement, the process approach and continual improvement. Generally, the ISO 9001 serves as a base standard that is compatible with other standards of different specific sectors and industries.

ISO standards are voluntary. However, some are mandatory if for example referenced in regulation. These regulations differ across countries. For instance, the ISO 7010 standard for safety signs is accepted as the European Standard, which is mandatory for all EU countries [].

ISO standards are reviewed at least once every five years to ensure that the standards are relevant and up to date to the present market. This means the handbooks that were written using ISO standards as a starting point likewise need to be revised, so the new versions are updated in terms of ISO standards. Gradually, the handbook will contain numerous versions of documents. It is time consuming to manage and keep track of the current version manually without a version control system. 

% Definitions:
% Resources utilization definition: this measures ‘how’ effectively your company is making use of the available resources.
% Sustainability means meeting our own needs without compromising the ability of future generations to meet their own needs.
% Business vs Organization: A business is one sort of organization, with the specific purpose of making money (taking in more income than it is spending). Therefore we say a business is a ‘commercial’ organization. An organization in general simply means a group of people working together in some sort of organized set up, working toward common goals.
