\section{Usage}\label{sec:Usage}
\todo[inline]{Vejleders tidligere kommentar omkring Usage afsnit skal rettes til}

In this section the usage of the system will be analyzed. 
Who uses and how they use the system will be explored systematically through analyzing who the actors are, and the use cases of the system.
Both will be analyzed with an abstraction level to be able to see the more broad uses of the system.
%Anna: What abstraction level.
The actors consists of the different user groups who will be utilizing the system and the use cases will describe the different uses the system will potentially have.

The actors that have been identified within the case are \textit{consultant, secretary, manager, worker}, and \textit{document management software}.
%Anna: Hvorfor er quality manager ikke en del af use case analysen
It should be noted here that the software in this context refers to the software that is under development throughout this project.
This will outline what responsibilities that the system will eventually have when it is deployed.
The use cases of the system have been identified to be \textit{manage documents, manage users, manage departments, manage suppliers, approve new documents, read status, update Table of Contents}, and \textit{track differences between document versions}.

An overview of the relationships between the actors and the use cases are shown through the table below, \cref{tab:UseCases}.
Here it is outline which actors have which responsibilities in relation to the system.

%Anna: Snakker virkeligt om consulenter (ikke fordi vi ikke godt kan) men hvorfor da det jo er meget forskelligt hvilke rettigheder en konsulent vil have?
\begin{table}[H]
	\begin{center}
	\begin{tabular}{| m{10em} | c | c | c | c | c |}
		\hline
		& \multicolumn{5}{c|}{\textbf{Actors}} \\
		\hline
		\textbf{Use cases} & Consultant & Secretary & Manager & Worker & Software \\
		\hline
		Manage documents & x & & & & x \\
		\hline
		Manage users & & x & & & \\
		\hline
		Manage departments & & x & & & x \\
		\hline
		Manage suppliers & x & x & x & &\\
		\hline
		Approve new docs & & x & x & & \\
		\hline
		Update TOC & & & & & x \\
		\hline
		Track differences\newline between document\newline versions & x & x & & &\\
		\hline
	\end{tabular}
	\end{center}
	\caption{ {\color{red}husk at sætte caption og label så den kan referes til} }\label{tab:UseCases}
\end{table}
%Tænker at vi er nødt til at tilføje en use case omkring at læse dokumenter eller noget fordi det ikke rigtigt giver mening at have en aktør der intet kan.

In the rest of this section both the actors and use cases will be elaborated, starting with the actors.

\subsection{Actors}

\textbf{Consultant}
\\%Indsat af Anna for at fjerne ekstra linjeskift
Goal: A 3rd party person who helps with writing and managing documents.
\\ %Anna: eller bare tjekker op på systemet, eller hvad der ellers er brug for
Characteristic: There is only one consultant who has intimate knowledge about the documents and their versions.
\\ %Anna: Vel ikke nødvendigvis, et firma kan velsagtens have flere konsulenter
Examples: One or more times a year a document has to be updated. 
The updated documents gets written, depending on the firm it is logged why the new document is updated and it’s highlighted exactly where the changes has occurred.
%Anna: den highlighting som Pia bruer er vel ikke noget alle gør det er bare noget hun gør for nememre at kunne sige hvor forskellene ligger

\textbf{Secretary}
\\
Goal: An administrative personnel working within the firm who manages documents in the handbook and the users of the system.
\\%Anna: sectretary manger vel som sådan ikke documents? skal bare kunne finde ting i arkivet og ellers administrere userne
Characteristic: There’s usually only one secretary with intimate knowledge of the handbook, the system, and the firm. 
The secretary has a lot of responsibility of the handbook and users within the system.
\\%Anna: Igen ligger hendes responsibility virkeligt ift handbooken
Examples: The secretary manages the users by creating a user in the system, edits the user, and eventually deletes a user.
The secretary also creates groups of users who are subscribed to relevant documents within the handbook.
%Anna: Sidste del var det ikke et punkt som var mere relevant for wquality manageren end for Pia (eller generelt dem der skriver), Anerkender godt at secretary nok oftest er med til at adde users til departments, men ud over det gør hun vel ikke mere med den del af systemet
%Jeg tænker lige at vi skal diskutere hvem sekretæren er for vi har vist forskellige opfattelser -astrid

\textbf{Manager}
\\%Anna: Mener vi department managers eller som taniya påpeger nedenunder direktøren?
Goal: The manager of the firm.
\\
Characteristic: There is only one manager.
The manager does not have intimate knowledge of the system and do not administrate the handbook.
% Taniya: only one manager? Måske at det er bedre med "director"?
Characteristic: There’s only one manager. 
The manager doesn’t have intimate knowledge of the system and doesn’t administrate the handbook.
The manager may change and/or approve documents every once in a while.
\\
Examples: The manager reads and sometimes approves documents.

\textbf{Worker}
\\
Goal: A person who works within the firm.
\\%Anna: works within the firm and production???
Characteristic: There are several workers within the firm. 
They typically do not have administrative rights and don’t write or update the documents within the handbook. 
There are different kinds of workers with varying jobs and work in different departments.
\\
Examples: Whenever a relevant document has been updated it is imperative that the worker has read and understood the new version.
Sometimes a worker may have the responsibility of approving one or more documents.

\textbf{Software}
\\%Anna: Er vi sikker på vil have denne del med som actor
Goal: Manages document versions within a handbook and users.
\\
Characteristic: 
Is a software that can be accessed and used by different users with varying degrees of administrative rights.
\\
Examples: Keeps track of document versions; including which documents are active, and which are inactive and by extension are archived. 
When a document has been updated it is possible for the user to log why there are changes and the system is able to highlight exactly where the changes has occurred.
%Taniya: er det ikke mens man er i gang med at upload en ny version at man tilføjer en changelog og ikke efterfølgende?
%Anna: Systemet som vi laver markerer ikke forskelle det er en drøm fra Pia men ikke noget dette projekt development gør.
Whenever a new document has been added the TOC is updated.
The system manages users with varying degrees of administrative rights of which there are 3 levels.


\subsection{Use cases} \label{sec:usecases}
%Anna: evt fjern "use case:" fra hvert punkt i denne subsection
%Astrid: Use cases her virker umiddelbart generelt ikke helt konkrete nok? vi mangler også statechart diagrammer men jeg ved ikke om det er noget vi har tænkt os at gøre noget ved.
\textbf{Manage documents}
\\
It is desired that a handbook containing several documents and their versions is managed by a software. 
This includes a table of contents from which users are able to have an overview of the documents. 
%Anna: er der ikke tidligere blevet lagt klart at table of contents er TOC?
There are active and inactive documents, where the active documents consists of the newest versions of the documents, and inactive ones are archived. 
Whenever a document has been updated, the system is responsible for highlighting exactly where the change has occurred. 
%anna: igen samme kommentar som ovenfor, synes denne del er farlig at skrive, medmindre vi explicit afgrænser os væk fra det.
The system also provides the consultant or secretary with the option to write a changelog, where the user can write why there are changes to the document.
%Det er vel i virkeligheden, alle med writer acces så både writer og administrator (hvilket ikke nødvendigvis er en consulent)

\textbf{Manage users}
\\
It is the secretary and software's responsibility to manage users and their administrative rights.
The secretary updated the system with adding, editing or removing users, while the software stores the users and their data in a database.
%Anna: hvilken tid skrives der i?
There are three types of users with varying degrees of administrative rights.
The secretary who has administrative rights within the system keeps tracks of the users and suppliers with their respective administrative rights.
%Anna: Igen ikke rigtigt secretaryen som tracker suppliers, og denne del er vi også afgrænset væk fra
The secretary is able to create, edit, and delete users.
%Tidligere oppe står der: The secretary can remove users og til sidst står der archive users. Kan ikke huske hvad vi blev enige om det med at fjerne en bruger

\textbf{Manage departments}
\\%Anna: Igen det er ikke kune secretaryien det er administratoren så også noget quality manager gør
The secretary manages departments within the system.
The secretary is able to create, edit, and delete departments by adding or removing users from them.
A department is subscribed to one or more documents which are relevant to the users within the department.
A user can be within one or more departments at once.
The software is responsible for notifying the departments whenever a document has been updated.

\textbf{Manage suppliers}
\\
The consultant and secretary manages the suppliers. Help.
%Suppliers skal vist slet ikke nævnes i usage afsnit? Fordi vi afgrænser os væk fra suppliers i class diagram afsnit?
%Anja: Tjoh

\textbf{Approve new documents}
\\
Whenever a new version of a document is available, it needs to be approved by one or more persons.
The user(s) who is responsible for approving the document(s) could either be the manager, worker, or a 3rd party supplier.
%Anna: supplier kan ikke godkende, men igen mangler quality manager, ellers evt bare skrive alle i systemet
When a document has been approved it is updated within the system, the older document is archived and the TOC is updated.

\textbf{Read status}
\\
Whenever an updated document is available, the subscribed departments are alerted.
All users within the subscribed department must read and understand the new document version.
When this is done, they check off box which indicates to the system and secretary that the new document has been read.


\textbf{Update TOC}
\\
When a new document version is available the TOC is being updated.
% Opdatering af TOC står også under Approve mew documents. Spørgsmål er bør den have sin egen lille use case.
%Anna: casen virker i hvert fald lidt tynd alene

\textbf{Track versions between documents}
\\
It is important to track the document versions and the changes within.
Both the consultant and secretary are responsible of writing in the handbook and keep track of changes.
It is the consultant's and secretary’s responsibility to write a changelog, if it is required within the firm, and highlight relevant differences between versions.
%Det er vel ikke deres ansvar, de skal bare sikre det sker, men er vel den der skrivers ansvar

% Henrik: Er det ikke quality manager der er administrator?
% Henrik: Det er ihvertfald det indtryk jeg har fået igennem rapporten indtil videre
% Henrik: Der skal generelt henvises til tidligere tekst + er lidt forvirret mht "consultant"
