\section{Third iteration}
\subsection{Simple timeline}\label{sec:3Iteration-timeline}
The third iteration started with the evaluation activity from \cref{fig:DEBModel} based upon the fifth meeting with Ipsen, where the interactive prototype, with added functionality, and the mock-up design were presented.
At the end of the evaluation activity the work proccess flowed into a combination of the design and envisionment activities as well as the understanding activity.
The combination of design and activity was mainly used when further developing the mock-up.
As for the understanding activity, this was used mainly in combination with the evaluation activity when revisiting the analysis and design of the system.

During the iteration the class diagram belonging to the Porblem domain in \cref{fig:SUModels} was evolved to its final evolution presented in this report, see \cref{fig:ClassDiagramNoSupplier}.
This diagram indicating the actual sub-problem being in focus of this report.
The workflow also went through the apllication domain activity seen in. 
During this process, the function list, actors and use cases were revisited 
Furthermore the third iteration also included a visit to the architectual design and component design activities.
Until this point these activities had been shortly discussed and sketched.
Though in this iteration the elements in these activities were more thoroughly designed and worked upon.
Leading to the results seen in \cref{sec:architecturecriteria,sec:AppMethod,sec:componentdesign}.
Parallel with this workflow the design process on the Mock-up continued.

Iteration three ended with a usability test done with Ipsen and her immediate family as test subjects. 
Followed by a short discussion with Ipsen about the system in general.



\subsection{Elements to take notice of}
\subsubsection*{Actors and use-cases}
\subsubsection*{Some conclusions on last prototype}

\subsubsection*{Further prototype development}