\section{Why testing is important} \label{sec:whytesting}
% Hvorfor
% Rasmus: Hmm. skal vi, når vi går på datalogi, argumentere for hvorfor software er vigtigt?
%Anna: vil næten netop argumenterer for at netop fordi vi går på det her studie er det relevant at argumenterr for (da det også især man kan se ud i sammenhængen)
% Indledningen er muligvis lidt for lang
Software has, in modern times, infiltrated almost everything that we do \cite{SoftwareTesting}.
It is easy to see that software has infiltrated our lives when walking outside and observing people in the street.
A lot of those people are using their phones, either talking in it or, texting, checking their social medias or playing games.
Another place, where it is easy to see that software has infiltrated our lives, is our hospitals.
Hospitals have e.g. MRI-scanner, CT-scanner and vital sign monitors (VSM).
Here it is very important that the software used by those devices is thoroughly tested to make sure that it works as it should.

% Software er lavet af mennesker og derfor ikke perfekt
Another reason why it is important to test software is because it is written by people and it is therefore not perfect \cite{SoftwareTesting}.

% Eksempel med Disney fra bogen
A great example to illustrate what can happen if software is not tested thoroughly enough before being released is when Disney released a multimedia CD-ROM game, \textit{The Lion King Animated Storybook}, in $1994$.
It was a very popular Christmas present for kids that year.
The phone technicians were swamped with calls from angry parents on december 26, the day after Christmas.
The reason for this was that they could not get the software to work. %\cite{SoftwareTesting}
It turned out that the developers at Disney had not tested the software on a broad representation of the many different PC models available on the market.
This resulted in a software that only worked on the systems used at Disney and not the most common systems which the customers used. \cite{SoftwareTesting}
%Anna: Kan virkeligt godt lide eksemplet men tænker godt vi kan cutte hele afsnittet ovenfor
% Henrik: Er stærkt uenig

% Rasmus: Hmm. I mean, it's very possible to have a function with a limited input space, which you could test completely?
% Henrik: Som hvad fx.? - anyway, det er bare hvad der staar i bogen :-)
Even though it is important to thoroughly test software it is important to keep in mind that it is not possible to test a software $100\%$.
This is because of the large number of possible inputs, outputs and paths through the software.
It can also be because that the specification is too subjective and, therefore, what is defined as an error varies from one tester to another. \cite{SoftwareTesting}
